Supporting Information for ``The dynamics of starvation and recovery''

### 2017-02-09 Manuscript/Yield-Constants-Calculation-3.tex
new yield constants

\section*{Explicit Consumption Derivation}
If I were to write out an explicit mass balance for our system in a dimensional system it would be:
\begin{align} 
\begin{split}
\dot{F} &= \lambda\left(R\right) F + \rho\left(R\right)H - \sigma \left(1-\frac{R}{C}\right)F,  \\
\dot{H} &= \sigma \left(1-\frac{R}{C}\right)F - \rho\left(R\right)H - \mu H,  \\
\dot{R} &= \alpha R\left(1-\frac{R}{C}\right) -\left[\left(\frac{\rho\left(R\right)}{Y}+P\right)H+\left(\frac{\lambda\left(R\right)}{Y}+P\right)F\right]
\end{split}
\end{align}
(note this is not fully explicit because I don't know how to deal with the response of $\sigma$ to resources, although I have an idea for a derivation which may be necessary given the following approximations), where $\lambda\left(R\right)$ and $\rho\left(R\right)$ are the growth and recovery functions dependent on resource availability. Typically these can be written as $\lambda\left(R\right)=\lambda_{max}S\left(R\right)$ where $\lambda_{max}$ is the maximum growth rate which changes with size, and $S\left(R\right)$ is a saturating function of resources, for example a Michealis-Menten or Monod function of the form $\frac{R}{k_{H}+R}$.  In these equations $Y$ represents the quantity of resources required to build a unit of organism (e.g. gram of mammal produced per gram of grass consumed) and $P$ is the specific maintenance rate of resource consumption (g resource $\cdot$ s$^{-1}$ $\cdot$ g organism). If we pick $F$ and $H$ to have units of (g organisms $\cdot$ m$^{-2}$), then terms like $\frac{\rho\left(R\right)}{Y}H$ have units of (g resource $\cdot$ m$^{-2}$ $\cdot$ s$^{-1}$) which is just the net primary productivity (NPP), a natural unit for $\dot{R}$, and this also gives us the units of $R$ as (g $\cdot$ m$^{-2}$) which is also a natural unit and is just the biomass density. In this system of units $\alpha$ is the growth rate of $R$. First, before diving into the constant values and a general nondimensionalization, let's look at the limits of the above equations in relationship to our two-state model: The saturation function should be defined by a linear regime proportional to $R$ when $R<<k$ and a constant value for $R>>k$. Thus for starving individuals, where $R<<k$, we have that $\rho\left(R\right)=\rho_{max}R/k$, and for the full class or organisms $\lambda\left(R\right)=\lambda_{max}$ such that the above relationships reduce to
\begin{align} 
\begin{split}
\dot{F} &= \lambda_{max} F + \rho_{max}RH/k - \sigma \left(1-\frac{R}{C}\right)F,  \\
\dot{H} &= \sigma \left(1-\frac{R}{C}\right)F - \rho_{max}R H/k - \mu H,  \\
\dot{R} &= \alpha R\left(1-\frac{R}{C}\right) -\left[\left(\frac{\rho_{max}R}{Yk}+P\right)H+\beta F\right]
\end{split}
\end{align}
where $\beta=\frac{\lambda_{max}}{Y}+P$ which is just a constant that depends on the size of an organisms via the allometries for $\lambda_{max}$ and $P$.

Now consider the following nondimensionalization (ignoring the $\sigma (1-R)F$ terms which I don't have a dimensional form for yet),: $F^{*}=fF$, $H^{*}=fH$, $R^{*}=qR$, $t^{*}=st$ then we would have:
\begin{align} 
\begin{split}
\dot{F}^{*} &= \frac{1}{s}\left[\lambda_{max} F^{*} + \rho_{max}\frac{R^{*}}{qk}H^{*} - \sigma \left(1-\frac{R^{*}}{qC}\right)F^{*}\right],  \\
\dot{H}^{*} &= \frac{1}{s}\left[\sigma \left(1-\frac{R^{*}}{qC}\right)F^{*} - \rho_{max}\frac{R^{*}}{qk} H^{*} - \mu H^{*}\right],  \\
\dot{R}^{*} &= \frac{1}{s}\left[\alpha R^{*}\left(1-\frac{R^{*}}{qC}\right) -\frac{q}{f}\left[\left(\frac{\rho_{max}R^{*}}{Ykq}+P\right)H^{*}+\beta F^{*}\right]\right]
\end{split}
\end{align}
Now there is a choice of factors that provides us with our original set of equations: if we pick $s=1$, $q=1/C$, and $f=1/Yk$, then we are left with 
\begin{align} 
\begin{split}
\dot{F}^{*} &= \lambda_{max} F^{*} + \rho_{2}R^{*}H^{*} - \sigma \left(1-R^{*}\right)F^{*},  \\
\dot{H}^{*} &= \sigma \left(1-R^{*}\right)F^{*} - \rho_{2} R^{*}H^{*} - \mu H^{*},  \\
\dot{R}^{*} &= \alpha R^{*}\left(1-R^{*}\right) -\left(\rho_{2}R^{*}+P_{2}\right)H^{*}-\beta_{2} F^{*}
\end{split}
\end{align}
where $\rho_{2}=C\rho_{max}/k$, $P_{2}=YkP/C$, and $\beta_{2}=Yk\beta/C$. Typically the value of $C/k$ should roughly be $2$. A summary of the parameters values is then: $\rho_{2}=$ 2 times our old $\rho$; $\lambda$, $\sigma$, and $\mu$ are all unchanged (the max notation can be dropped here and equated with the old values). Now $P=B_{0}m^{3/4}$, and $Y=18200$ (J g$^{-1}$) for grass \cite{estermann} which allows us to calculate $P_{2}=YB_{0}m^{3/4}/2$ and $\beta_{2}=Y/2$ (note again that $\beta=\frac{\lambda_{max}}{Y}+P$, and $\lambda_{max}$ is our old value for $\lambda$) . Finally, the value of $\alpha$ is given by the NPP divided by the corresponding biomass densities which I find to be $\alpha=2.10\times10^{-9}$ (s$^{-1}$) in a database that I have.

>>>>

\section*{Explicit Consumption Derivation}
If I were to write out an explicit mass balance for our system in a dimensional system it would be:
\begin{align} 
\begin{split}
\dot{F} &= \lambda\left(R\right) F + \rho\left(R\right)H - \sigma \left(1-\frac{R}{C}\right)F,  \\
\dot{H} &= \sigma \left(1-\frac{R}{C}\right)F - \rho\left(R\right)H - \mu H,  \\
\dot{R} &= \alpha R\left(1-\frac{R}{C}\right) -\left[\left(\frac{\rho\left(R\right)}{Y}+P\right)H+\left(\frac{\lambda\left(R\right)}{Y}+P\right)F\right]
\end{split}
\end{align}
(note this is not fully explicit because I don't know how to deal with the response of $\sigma$ to resources, although I have an idea for a derivation which may be necessary given the following approximations), where $\lambda\left(R\right)$ and $\rho\left(R\right)$ are the growth and recovery functions dependent on resource availability. Typically these can be written as $\lambda\left(R\right)=\lambda_{max}S\left(R\right)$ where $\lambda_{max}$ is the maximum growth rate which changes with size, and $S\left(R\right)$ is a saturating function of resources, for example a Michealis-Menten or Monod function of the form $\frac{R}{k_{H}+R}$.  In these equations $Y$ represents the quantity of resources required to build a unit of organism (e.g. gram of mammal produced per gram of grass consumed) and $P$ is the specific maintenance rate of resource consumption (g resource $\cdot$ s$^{-1}$ $\cdot$ g organism). If we pick $F$ and $H$ to have units of (g organisms $\cdot$ m$^{-2}$), then terms like $\frac{\rho\left(R\right)}{Y}H$ have units of (g resource $\cdot$ m$^{-2}$ $\cdot$ s$^{-1}$) which is just the net primary productivity (NPP), a natural unit for $\dot{R}$, and this also gives us the units of $R$ as (g $\cdot$ m$^{-2}$) which is also a natural unit and is just the biomass density. In this system of units $\alpha$ is the growth rate of $R$. First, before diving into the constant values and a general nondimensionalization, let's look at the limits of the above equations in relationship to our two-state model: The saturation function should be defined by a linear regime proportional to $R$ when $R<<k$ and a constant value for $R>>k$. Thus for starving individuals, where $R<<k$, we have that $\rho\left(R\right)=\rho_{max}R/k$, and for the full class or organisms $\lambda\left(R\right)=\lambda_{max}$ such that the above relationships reduce to
\begin{align} 
\begin{split}
\dot{F} &= \lambda_{max} F + \rho_{max}RH/k - \sigma \left(1-\frac{R}{C}\right)F,  \\
\dot{H} &= \sigma \left(1-\frac{R}{C}\right)F - \rho_{max}R H/k - \mu H,  \\
\dot{R} &= \alpha R\left(1-\frac{R}{C}\right) -\left[\left(\frac{\rho_{max}R}{Y_{H}k}+P\right)H+\beta F\right]
\end{split}
\end{align}
where $\beta=\frac{\lambda_{max}}{Y_{F}}+P$ which is just a constant that depends on the size of an organisms via the allometries for $\lambda_{max}$ and $P$. A natural system of units for this system is that $R$ is a resource density (g m$^{-2}$) and $F$ and $H$ are the density of individuals (individuals m$^{-2}$). Given these definitions, $Y$ is the amount of resources required for an organism to grow to maturity (g resource individual$^{-1}$).

Now consider the following nondimensionalization (ignoring the $\sigma (1-R)F$ terms which I don't have a dimensional form for yet),: $F^{*}=fF$, $H^{*}=fH$, $R^{*}=qR$, $t^{*}=st$ then we would have:
\begin{align} 
\begin{split}
\dot{F}^{*} &= \frac{1}{s}\left[\lambda_{max} F^{*} + \rho_{max}\frac{R^{*}}{qk}H^{*} - \sigma \left(1-\frac{R^{*}}{qC}\right)F^{*}\right],  \\
\dot{H}^{*} &= \frac{1}{s}\left[\sigma \left(1-\frac{R^{*}}{qC}\right)F^{*} - \rho_{max}\frac{R^{*}}{qk} H^{*} - \mu H^{*}\right],  \\
\dot{R}^{*} &= \frac{1}{s}\left[\alpha R^{*}\left(1-\frac{R^{*}}{qC}\right) -\frac{q}{f}\left[\left(\frac{\rho_{max}R^{*}}{Y_{H}kq}+P\right)H^{*}+\beta F^{*}\right]\right]
\end{split}
\end{align}
Now there is a choice of factors that provides us with our original set of equations: if we pick $s=1$, $q=1/C$, and $f=1/Y_{H}k$, then we are left with 
\begin{align} 
\begin{split}
\dot{F}^{*} &= \lambda_{max} F^{*} + \rho_{2}R^{*}H^{*} - \sigma \left(1-R^{*}\right)F^{*},  \\
\dot{H}^{*} &= \sigma \left(1-R^{*}\right)F^{*} - \rho_{2} R^{*}H^{*} - \mu H^{*},  \\
\dot{R}^{*} &= \alpha R^{*}\left(1-R^{*}\right) -\left(\rho_{2}R^{*}+P_{2}\right)H^{*}-\beta_{2} F^{*}
\end{split}
\end{align}
where $\rho_{2}=C\rho_{max}/k$, $P_{2}=Y_{H}kP/C$, and $\beta_{2}=Y_{H}k\beta/C$. Typically the value of $C/k$ should roughly be $2$. A summary of the parameters values is then: $\rho_{2}=$ 2 times our old $\rho$; $\lambda$, $\sigma$, and $\mu$ are all unchanged (the max notation can be dropped here and equated with the old values). Consider an energy density of $E_{d}=18200$ (J g$^{-1}$) for grass \cite{estermann} then the maintenance values is given by $P=B_{0}M^{3/4}/ME_{d}$, and the yield for a full organism will be given by $Y_{F}=ME_{d}/B_{\lambda}$ (g individual $\cdot$ g grass $^{-1}$) where $B_{\lambda}$ is the lifetime energy use for reaching maturity given by 
\begin{equation}
B_{\lambda}=\int_{0}^{t_{\lambda}}B_{0}m\left(t\right)^{\eta}dt.
\end{equation}
Similarly, the yield for hungry individuals (representing the cost on resources to return to the full state) is given by $Y_{H}=ME_{d}/B_{\lambda}$ where
\begin{equation}
B_{\rho}=\int_{\tau\left(\epsilon_{\sigma}\epsilon_{\lambda}\right)}^{t_{\lambda}}B_{0}m\left(t\right)^{\eta}dt.
\end{equation}
which allows us to calculate $P_{2}=Y_{H}B_{0}M^{3/4}/2ME_{d}$ and $\beta_{2}=Y_{H}\beta/2$ (note again that $\beta=\frac{\lambda_{max}}{Y_{F}}+P$, and $\lambda_{max}$ is our old value for $\lambda$) . Finally, the value of $\alpha$ is given by the NPP divided by the corresponding biomass densities which I find to be $\alpha=2.10\times10^{-9}$ (s$^{-1}$) in a database that I have.

### 2017-02-09 Manuscript/Yield-Constants-Calculation.tex
new yield constants

\section*{Explicit Consumption Derivation}
If I were to write out an explicit mass balance for our system in a dimensional system it would be:
\begin{align} 
\begin{split}
\dot{F} &= \lambda\left(R\right) F + \rho\left(R\right)H - \sigma \left(1-\frac{R}{C}\right)F,  \\
\dot{H} &= \sigma \left(1-\frac{R}{C}\right)F - \rho\left(R\right)H - \mu H,  \\
\dot{R} &= \alpha R\left(1-\frac{R}{C}\right) -\left[\left(\frac{\rho\left(R\right)}{Y}+P\right)H+\left(\frac{\lambda\left(R\right)}{Y}+P\right)F\right]
\end{split}
\end{align}
(note this is not fully explicit because I don't know how to deal with the response of $\sigma$ to resources, although I have an idea for a derivation which may be necessary given the following approximations), where $\lambda\left(R\right)$ and $\rho\left(R\right)$ are the growth and recovery functions dependent on resource availability. Typically these can be written as $\lambda\left(R\right)=\lambda_{max}S\left(R\right)$ where $\lambda_{max}$ is the maximum growth rate which changes with size, and $S\left(R\right)$ is a saturating function of resources, for example a Michealis-Menten or Monod function of the form $\frac{R}{k_{H}+R}$.  In these equations $Y$ represents the quantity of resources required to build a unit of organism (e.g. gram of mammal produced per gram of grass consumed) and $P$ is the specific maintenance rate of resource consumption (g resource $\cdot$ s$^{-1}$ $\cdot$ g organism). If we pick $F$ and $H$ to have units of (g organisms $\cdot$ m$^{-2}$), then terms like $\frac{\rho\left(R\right)}{Y}H$ have units of (g resource $\cdot$ m$^{-2}$ $\cdot$ s$^{-1}$) which is just the net primary productivity (NPP), a natural unit for $\dot{R}$, and this also gives us the units of $R$ as (g $\cdot$ m$^{-2}$) which is also a natural unit and is just the biomass density. In this system of units $\alpha$ is the growth rate of $R$. First, before diving into the constant values and a general nondimensionalization, let's look at the limits of the above equations in relationship to our two-state model: The saturation function should be defined by a linear regime proportional to $R$ when $R<<k$ and a constant value for $R>>k$. Thus for starving individuals, where $R<<k$, we have that $\rho\left(R\right)=\rho_{max}R/k$, and for the full class or organisms $\lambda\left(R\right)=\lambda_{max}$ such that the above relationships reduce to
\begin{align} 
\begin{split}
\dot{F} &= \lambda_{max} F + \rho_{max}RH/k - \sigma \left(1-\frac{R}{C}\right)F,  \\
\dot{H} &= \sigma \left(1-\frac{R}{C}\right)F - \rho_{max}R H/k - \mu H,  \\
\dot{R} &= \alpha R\left(1-\frac{R}{C}\right) -\left[\left(\frac{\rho_{max}R}{Y_{H}k}+P\right)H+\beta F\right]
\end{split}
\end{align}
where $\beta=\frac{\lambda_{max}}{Y_{F}}+P$ which is just a constant that depends on the size of an organisms via the allometries for $\lambda_{max}$ and $P$. A natural system of units for this system is that $R$ is a resource density (g m$^{-2}$) and $F$ and $H$ are the density of individuals (individuals m$^{-2}$). Given these definitions, $Y$ is the amount of resources required for an organism to grow to maturity (g resource individual$^{-1}$).

Now consider the following nondimensionalization (ignoring the $\sigma (1-R)F$ terms which I don't have a dimensional form for yet),: $F^{*}=fF$, $H^{*}=fH$, $R^{*}=qR$, $t^{*}=st$ then we would have:
\begin{align} 
\begin{split}
\dot{F}^{*} &= \frac{1}{s}\left[\lambda_{max} F^{*} + \rho_{max}\frac{R^{*}}{qk}H^{*} - \sigma \left(1-\frac{R^{*}}{qC}\right)F^{*}\right],  \\
\dot{H}^{*} &= \frac{1}{s}\left[\sigma \left(1-\frac{R^{*}}{qC}\right)F^{*} - \rho_{max}\frac{R^{*}}{qk} H^{*} - \mu H^{*}\right],  \\
\dot{R}^{*} &= \frac{1}{s}\left[\alpha R^{*}\left(1-\frac{R^{*}}{qC}\right) -\frac{q}{f}\left[\left(\frac{\rho_{max}R^{*}}{Y_{H}kq}+P\right)H^{*}+\beta F^{*}\right]\right]
\end{split}
\end{align}
Now there is a choice of factors that provides us with our original set of equations: if we pick $s=1$, $q=1/C$, and $f=1/Y_{H}k$, then we are left with 
\begin{align} 
\begin{split}
\dot{F}^{*} &= \lambda_{max} F^{*} + \rho_{2}R^{*}H^{*} - \sigma \left(1-R^{*}\right)F^{*},  \\
\dot{H}^{*} &= \sigma \left(1-R^{*}\right)F^{*} - \rho_{2} R^{*}H^{*} - \mu H^{*},  \\
\dot{R}^{*} &= \alpha R^{*}\left(1-R^{*}\right) -\left(\rho_{2}R^{*}+P_{2}\right)H^{*}-\beta_{2} F^{*}
\end{split}
\end{align}
where $\rho_{2}=C\rho_{max}/k$, $P_{2}=Y_{H}kP/C$, and $\beta_{2}=Y_{H}k\beta/C$. Typically the value of $C/k$ should roughly be $2$. A summary of the parameters values is then: $\rho_{2}=$ 2 times our old $\rho$; $\lambda$, $\sigma$, and $\mu$ are all unchanged (the max notation can be dropped here and equated with the old values). Consider an energy density of $E_{d}=18200$ (J g$^{-1}$) for grass \cite{estermann} then the maintenance values is given by $P=B_{0}M^{3/4}/ME_{d}$, and the yield for a full organism will be given by $Y_{F}=ME_{d}/B_{\lambda}$ (g individual $\cdot$ g grass $^{-1}$) where $B_{\lambda}$ is the lifetime energy use for reaching maturity given by 
\begin{equation}
B_{\lambda}=\int_{0}^{t_{\lambda}}B_{0}m\left(t\right)^{\eta}dt.
\end{equation}
Similarly, the yield for hungry individuals (representing the cost on resources to return to the full state) is given by $Y_{H}=ME_{d}/B_{\lambda}$ where
\begin{equation}
B_{\rho}=\int_{\tau\left(\epsilon_{\sigma}\epsilon_{\lambda}\right)}^{t_{\lambda}}B_{0}m\left(t\right)^{\eta}dt.
\end{equation}
which allows us to calculate $P_{2}=Y_{H}B_{0}M^{3/4}/2ME_{d}$ and $\beta_{2}=Y_{H}\beta/2$ (note again that $\beta=\frac{\lambda_{max}}{Y_{F}}+P$, and $\lambda_{max}$ is our old value for $\lambda$) . Finally, the value of $\alpha$ is given by the NPP divided by the corresponding biomass densities which I find to be $\alpha=2.10\times10^{-9}$ (s$^{-1}$) in a database that I have.

%
% term reduces to $\rho_{max}/k_{H}RH$ which is what we had before except that $\rho_{max}$ has an extra constant in it. For full individuals,  $R>>k$ and the $\lambda_{max}\frac{R}{k_{F}+R} F$ term becomes simply $\lambda_{max}F$ which differs from our previous version of the last term in the third equation. We are justified in taking both of these limits at the same time because of how we are binning and defining nutritional state (Note: we can simulate the full dynamics with the $\frac{R}{k+R}$ terms and see how different things are).

%Now consider the following nondimensionalization (ignoring the $\sigma (1-R)F$ terms which I don't have a dimensional form for yet),: $F^{*}=fF$, $H^{*}=fH$, $R^{*}=qR$, $t^{*}=st$ then we would have:
%\begin{align} 
%\begin{split}
%\frac{\partial F^{*}}{\partial t^{*}} &= \frac{1}{s}\left(\lambda_{max}\frac{R^{*}}{k_{F}q+R^{*}} F^{*} + \rho_{max}\frac{R^{*}}{k_{H}q+R^{*}}H^{*}\right),  \\
%\frac{\partial H^{*}}{\partial t^{*}} &=  \frac{1}{s}\left(- \rho_{max}\frac{R^{*}}{k_{H}q+R^{*}}H^{*} - \mu H^{*}\right),  \\
%\frac{\partial R^{*}}{\partial t^{*}} &=  \frac{1}{s}\left[\alpha R^{*}\left(1-\frac{R^{*}}{qC}\right) -\frac{q}{f}\left(\frac{\rho_{max}}{Y}\frac{R^{*}}{k_{H}q+R^{*}}H^{*}+\frac{\lambda_{max}}{Y}\frac{R^{*}}{k_{F}q+R^{*}}F^{*}\right)\right].
%\end{split}
%\end{align}

%\begin{align} 
%\begin{split}
%\frac{\partial F^{*}}{\partial t^{*}} &=\lambda_{max}\frac{R^{*}}{k_{F}/C+R^{*}} F^{*} + \rho_{max}\frac{R^{*}}{k_{H}/C+R^{*}}H^{*},  \\
%\frac{\partial H^{*}}{\partial t^{*}} &=  - \rho_{max}\frac{R^{*}}{k_{H}/C+R^{*}}H^{*} - \mu H^{*},  \\
%\frac{\partial R^{*}}{\partial t^{*}} &=  \alpha R^{*}\left(1-R^{*}\right) -\left(\rho_{max}\frac{R^{*}}{k_{H}/C+R^{*}}H^{*}+\lambda_{max}\frac{R^{*}}{k_{F}/C+R^{*}}F^{*}\right).
%\end{split}
%\end{align}
%and taking the above limits we have 
%\begin{align} 
%\begin{split}
%\frac{\partial F^{*}}{\partial t^{*}} &=\lambda_{max}F^{*} + \frac{\rho_{max}C}{k_{H}}R^{*}H^{*},  \\
%\frac{\partial H^{*}}{\partial t^{*}} &=  - \frac{\rho_{max}C}{k_{H}}R^{*}H^{*} - \mu H^{*},  \\
%\frac{\partial R^{*}}{\partial t^{*}} &=  \alpha R^{*}\left(1-R^{*}\right) -\left(\frac{\rho_{max}C}{k_{H}}R^{*}H^{*}+\lambda_{max}F^{*}\right).
%\end{split}
%\end{align}
%In summary, this is exactly our original system of equations (again with a $\lambda F$ instead of a $\lambda RF$ term in the last equation; and without dealing with the $\sigma (1-R)F$ term) and the only modification is that $\rho$ is adjusted by a factor of $C/k_{H}$ which should just be equal to $2$, and $F^{*}$, $H^{*}$, and $R^{*}$ are unites.

>>>>

\section*{Explicit Consumption Derivation}
If I were to write out an explicit mass balance for our system in a dimensional system it would be:
\begin{align} 
\begin{split}
\dot{F} &= \lambda_{max}\frac{R}{k_{F}+R} F + \rho_{max}\frac{R}{k_{H}+R}H - \sigma (1-R)F,  \\
\dot{H} &= \sigma (1-R)F - \rho_{max}\frac{R}{k_{H}+R}H - \mu H,  \\
\dot{R} &= \alpha R\left(1-\frac{R}{C}\right) -\left(\frac{\rho_{max}}{Y}\frac{R}{k_{H}+R}H+\frac{\lambda_{max}}{Y}\frac{R}{k_{F}+R}F\right).
\end{split}
\end{align}
(note this is not fully explicit because I don't know how to deal with the response of $\sigma$ to resources, although I have an idea for a derivation which may be necessary given the following approximations), where the $\lambda_{max}$ and $\rho_{max}$ terms scale with size and represent the maximum rate under infinite resources, and the $k$ terms are define how fast rates saturate to the maximum. In these equations $Y$ represents the quantity of resources required to build a unit of organism (e.g. gram of mammal produced per gram of grass consumed) such that if we pick $F$ and $H$ to have units of (g organisms $\cdot$ m$^{-2}$), then terms like $\frac{\rho_{max}}{Y}\frac{R}{k_{H}+R}H$ have units of (g R $\cdot$ m$^{-2}$ $\cdot$ s$^{-1}$ $\cdot$ number of individuals) which is just the net primary productivity (NPP), a natural unit for $\dot{R}$, and this also gives us the units of $R$ as (g $\cdot$ m$^{-2}$) which is also a natural unit and is just the biomass density. In this system of units $\alpha$ is the growth rate of $R$. (Note: these equations ignore a constant maintenance rate which is easy to add in.) First, before diving into the constant values and a general nondimensionalization, let's look at the limits of the above equations in relationship to our two-state model: for starving individuals $R<<k$ and the $\rho_{max}\frac{R}{k_{H}+R}H$ term reduces to $\rho_{max}/k_{H}RH$ which is what we had before except that $\rho_{max}$ has an extra constant in it. For full individuals,  $R>>k$ and the $\lambda_{max}\frac{R}{k_{F}+R} F$ term becomes simply $\lambda_{max}F$ which differs from our previous version of the last term in the third equation. We are justified in taking both of these limits at the same time because of how we are binning and defining nutritional state (Note: we can simulate the full dynamics with the $\frac{R}{k+R}$ terms and see how different things are).

Now consider the following nondimensionalization (ignoring the $\sigma (1-R)F$ terms which I don't have a dimensional form for yet),: $F^{*}=fF$, $H^{*}=fH$, $R^{*}=qR$, $t^{*}=st$ then we would have:
\begin{align} 
\begin{split}
\frac{\partial F^{*}}{\partial t^{*}} &= \frac{1}{s}\left(\lambda_{max}\frac{R^{*}}{k_{F}q+R^{*}} F^{*} + \rho_{max}\frac{R^{*}}{k_{H}q+R^{*}}H^{*}\right),  \\
\frac{\partial H^{*}}{\partial t^{*}} &=  \frac{1}{s}\left(- \rho_{max}\frac{R^{*}}{k_{H}q+R^{*}}H^{*} - \mu H^{*}\right),  \\
\frac{\partial R^{*}}{\partial t^{*}} &=  \frac{1}{s}\left[\alpha R^{*}\left(1-\frac{R^{*}}{qC}\right) -\frac{q}{f}\left(\frac{\rho_{max}}{Y}\frac{R^{*}}{k_{H}q+R^{*}}H^{*}+\frac{\lambda_{max}}{Y}\frac{R^{*}}{k_{F}q+R^{*}}F^{*}\right)\right].
\end{split}
\end{align}
Now there is a choice of factors that provides us with our original set of equations: if we pick $s=1$, $q=1/c$, and $f=q/Y$, then we are left with 
\begin{align} 
\begin{split}
\frac{\partial F^{*}}{\partial t^{*}} &=\lambda_{max}\frac{R^{*}}{k_{F}/C+R^{*}} F^{*} + \rho_{max}\frac{R^{*}}{k_{H}/C+R^{*}}H^{*},  \\
\frac{\partial H^{*}}{\partial t^{*}} &=  - \rho_{max}\frac{R^{*}}{k_{H}/C+R^{*}}H^{*} - \mu H^{*},  \\
\frac{\partial R^{*}}{\partial t^{*}} &=  \alpha R^{*}\left(1-R^{*}\right) -\left(\rho_{max}\frac{R^{*}}{k_{H}/C+R^{*}}H^{*}+\lambda_{max}\frac{R^{*}}{k_{F}/C+R^{*}}F^{*}\right).
\end{split}
\end{align}
and taking the above limits we have 
\begin{align} 
\begin{split}
\frac{\partial F^{*}}{\partial t^{*}} &=\lambda_{max}F^{*} + \frac{\rho_{max}C}{k_{H}}R^{*}H^{*},  \\
\frac{\partial H^{*}}{\partial t^{*}} &=  - \frac{\rho_{max}C}{k_{H}}R^{*}H^{*} - \mu H^{*},  \\
\frac{\partial R^{*}}{\partial t^{*}} &=  \alpha R^{*}\left(1-R^{*}\right) -\left(\frac{\rho_{max}C}{k_{H}}R^{*}H^{*}+\lambda_{max}F^{*}\right).
\end{split}
\end{align}
In summary, this is exactly our original system of equations (again with a $\lambda F$ instead of a $\lambda RF$ term in the last equation; and without dealing with the $\sigma (1-R)F$ term) and the only modification is that $\rho$ is adjusted by a factor of $C/k_{H}$ which should just be equal to $2$, and $F^{*}$, $H^{*}$, and $R^{*}$ are unites.
